\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2020-07-06 doc/USER_MANUAL/04_creating_databases.tex
fixed a bug in decompose_mesh_MPI introduced when I added support for QKappa; removed an old sentence in the users manual that said that the internal mesher did not support PMLs (it now does)
corrects typo, default name is tomograpy_model.xyz for tomo models

\item [{\texttt{tomo}}] For a user-specified 3D isotropic model which uses
a tomographic model file \texttt{tomographic\_model.xyz} in directory
\texttt{DATA}. See Section \ref{sec:Using-tomographic}, for a discussion
on how to specify your own 3D tomographic model.
\end{description}
\end{description}

@@

boundary conditions for a regional simulation. Both fluids and elastic
solids are supported. Note that xmeshfem3d generated meshes do not support C-PML yet.

>>>>

\item [{\texttt{tomo}}] For a user-specified 3D isotropic model which uses
a tomographic model file \texttt{tomography\_model.xyz} in directory
\texttt{DATA}. See Section \ref{sec:Using-tomographic}, for a discussion
on how to specify your own 3D tomographic model.
\end{description}
\end{description}

@@

boundary conditions for a regional simulation. Both fluids and elastic solids are supported.
